Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-29 WSSSPE1_report/WSSSPE1_summary_report.tex
Adding a few paragraphs on "what are communities"

\subsection{What are communities?}
\subsection{Challenges of community}
include metrics for community success (e.g., more external
contributors than internal).
\subsection{Admirable scientific software communities}
\begin{itemize}
\item example communities
\item their (quick) origin stories.
\end{itemize}
\subsection{Resources for learning about software communities}
\begin{itemize}
\item academic fields studying communities (and software communities)
\item courses on online communities
\item books
\item need for software carpentry module on organizing communities?
\end{itemize}

>>>>

\subsection{What are communities?}

The workshop did not directly answer the question ``What are communities?'' but
instead a number of different answers were indirectly presented, through the
depiction of individuals and stakeholders in different aspects of the
scientific software lifecycle.  In broad strokes, however, scientific software
communities were generally accepted as consisting of individuals, often but not
always composed of scientist practitioners, that were working with some degree
of coordination toward a common goal enabled by software.

The discussion of development-focused communities centered around describing
methods of interaction between individuals and the scientific software.  The
first type of interaction was the development of a specific piece of software,
the second was a particular domain or discipline, and the final primary
type of interaction was around the development of applications built on a
particular piece of software that was perhaps developed by another group.  As
an example, in \cite{Hanwell_WSSSPE}, the community described is comprised of
both the for-profit company Kitware and the users and contributors to their
software packages such as VTK.  This structure, of the centralized development
of core infrastructure around which communities of individuals applying that
infrastructure and developing applications utilizing it, was similarly
reflected in \cite{Terrel_WSSSPE}, where the core scientific python ecosystem
is supported by a non-profit entity that fosters community investment in that
ecosystem.  In many ways, these two organizations (Kitware and NumFOCUS)
attempt to cross domain boundaries and provide support for both the
infrastructure and application sides of community building.

\subsection{Challenges of community}
include metrics for community success (e.g., more external
contributors than internal).
\subsection{Admirable scientific software communities}
\begin{itemize}
\item example communities
\item their (quick) origin stories.
\end{itemize}
\subsection{Resources for learning about software communities}
\begin{itemize}
\item academic fields studying communities (and software communities)
\item courses on online communities
\item books
\item need for software carpentry module on organizing communities?
\end{itemize}
